Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
fix typo
small edit

The median runtime for our benchmark set is $197$\,s, implying that half of
the controllers can be synthesised in less than $5$ minutes using our
present approach.  Overall the average synthesis time amounts to
approximately $30$ minutes.  With respect to RQ2 we consider these times
short enough to be of practical use to control engineers.  Regarding RQ1 we
further conclude that the two-stage verification engine is able to synthesise stable
controllers in the $12$ out of $15$ benchmarks, and can be complemented
using the one-stage engine for $2$ additional benchmarks, where
the inductive conjectures fail.  Both verification engines together enabled controller
synthesis for $14$ out of $15$ benchmarks.  For the $1$ remaining benchmark
our approach failed to synthesise a stable controller in the requested time
limits.  This can be addressed by either increasing the fixed point word
widths considered or using floating point arithmetic instead.  A link to the
full experimental environment, including scripts to reproduce the
experiment, all benchmarks and the CEGIS tool is provided in the
footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}

>>>>

The median runtime for our benchmark set is $197$\,s, implying that half of
the controllers can be synthesised in less than $5$ minutes using our
present approach.  Overall the average synthesis time amounts to
approximately $30$ minutes.  With respect to RQ2 we consider these times
short enough to be of practical use to control engineers.  Regarding RQ1 we
further conclude that the approach using a 
two-stage verification engine is able to synthesise stable
controllers in the $12$ out of $15$ benchmarks, and can be complemented
using the one-stage engine for $2$ additional benchmarks, where
the inductive conjectures fail.  Both verification engines together enabled controller
synthesis for $14$ out of $15$ benchmarks.  For the $1$ remaining benchmark
our approach failed to synthesise a stable controller in the requested time
limits.  This can be addressed by either increasing the fixed point word
widths considered or using floating point arithmetic instead.  A link to the
full experimental environment, including scripts to reproduce the
experiment, all benchmarks and the CEGIS tool is provided in the
footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}
